### 2018-12-05 tex/abstract.tex
Version sent to Pawan & Chris for review.

\begin{abstract}
    Submodular extensions of an energy function can be used to efficiently
    compute approximate marginals via variational inference. The accuracy of
    the marginals depends crucially on the quality of the submodular extension.
    To identify the best possible extension, we show an equivalence between the
    submodular extensions of the energy and the objective functions of linear
    programming (LP) relaxations for the corresponding MAP estimation problem.
    This allows us to (i) establish the worst-case optimality of the submodular
    extension for Potts model used in the literature; (ii) identify the
    worst-case optimal submodular extension for the more general class of
    metric labeling; and (iii) efficiently compute the marginals for the widely
    used dense CRF model with the help of a recently proposed Gaussian filtering method. Using synthetic and real data, we show that our approach provides comparable upper bounds on the log-partition function to those obtained using tree-reweighted message passing (TRW) in cases where the latter is computationally feasible. Importantly, unlike TRW, our approach provides the first practical algorithm to compute an upper bound on the dense CRF model.
\end{abstract}

>>>>

\begin{abstract}
    Submodular extensions of an energy function can be used to efficiently
    compute approximate marginals via variational inference. The accuracy of
    the marginals depends crucially on the quality of the submodular extension.
    To identify the best possible extension, we show an equivalence between the
    submodular extensions of the energy and the objective functions of linear
    programming (LP) relaxations for the corresponding MAP estimation problem.
    This allows us to (i) establish the worst-case optimality of the submodular
    extension for Potts model used in the literature; (ii) identify the
    worst-case optimal submodular extension for the more general class of
    metric labeling; (iii) efficiently compute the marginals for the widely
    used dense CRF model with the help of a recently proposed Gaussian
    filtering method; and (iv) identify the submodular extension based on an LP
    relaxation for the higher-order Potts model. Using synthetic and real data, we show that our approach provides comparable upper bounds on the log-partition function to those obtained using tree-reweighted message passing (TRW) in cases where the latter is computationally feasible. Importantly, unlike TRW, our approach provides the first practical algorithm to compute an upper bound on the dense CRF model.
\end{abstract}

### 2018-12-05 tex/paper.tex
Version sent to Pawan & Chris for review.

In this work, we establish a hitherto unknown connection between the submodular
extension of the Potts model proposed by Zhang et al.\citep{zhang2015higher}, and the
objective function of an accurate linear programming (LP) relaxation of the
corresponding MAP estimation problem~\citep{kleinberg2002approximation}. This
connection has three important practical consequences. First, it establishes
the accuracy of the submodular extension of the Potts model, via the
UGC-hardness worst-case optimality of the LP relaxation. Second, it provides an
accurate submodular extension of the hierarchical Potts model, via the LP
relaxation of the corresponding MAP estimation problem proposed
by Kleinberg and Tardos \citep{kleinberg2002approximation}. Since any metric can be accurately
approximated as a mixture of hierarchical Potts
models~\citep{bartal1996probabilistic, bartal1998approximating}, this result
also provides a computationally feasible algorithm for estimating the marginals
for metric labeling. Third, it establishes the equivalence between the
subgradient of the LP relaxation and the conditional gradient of the problem of
minimising the upper bound of the log-partition. This allows us to employ the
widely used dense CRF, since the subgradient of its LP relaxation can be
efficiently computed using a recently proposed modified Gaussian filtering
algorithm~\citep{ajanthan2017efficient}. As a consequence, we provide the first
efficient algorithm to compute an upper bound of the log-partition function of
dense CRFs. This provides complementary information to the popular mean-field
inference algorithm for dense CRFs, which computes a lower bound on the
log-partition ~\citep{koltun2011efficient}. We show that the quality of our
solution is comparable to tree reweighted message passing (TRW)
~\citep{wainwright2005new} for the case of sparse CRFs. Unlike our approach,
TRW is computationally infeasible for dense CRFs, thereby limiting its use in
practice. Using dense CRF models, we perform stereo matching on standard
data sets and obtain better results than \citep{koltun2011efficient}. The complete code is available at \url{https://github.com/pankajpansari/denseCRF}.

@@

\begin{figure}
\centering
\includegraphics[scale = 0.30]{./figures/potts_chain_extension.png}
\mycaption{\footnotesize \em An illustration of the worst-case optimal
submodular extension for Potts model for a chain graph of 4 variables, each of
which can take 3 labels. The figure shows the way to compute the extension
values of the set $A = \{v_{1, 1}, v_{4, 1}, v_{3, 2}$\}.}
\label{fig:alternate}
\end{figure}
\begin{figure}
\centering
\resizebox{150pt}{120pt}{
\begin{tikzpicture}[-latex ,auto, node distance =1.5 cm and 1.5cm ,on grid
  , semithick , state/.style ={ circle , color = black , draw,black , text=blue , minimum width =1 cm}, cross/.style={color=red, very thick, dashed}, unary/.style={color=blue, very thick}]

@@

\myparagraph{Set Encoding} We choose to use the $1$-of-$L$ encoding for Potts model as described in section \ref{sec:review}. With the encoding scheme for Potts model above, $g({\bf s})$ can be factorised and problem (\ref{eq:min_upper_bound}) can be rewritten as:
%
\begin{equation}
\min_{{\bf s} \in EP(F)} \quad \sum_{a = 1}^{N} \log \sum_{i = 1}^L \exp(-s_{ai}).
\label{eq:potts_upper_bound}
\end{equation}
(See Remark 1 in appendix)
\myparagraph{Marginal Estimation with Temperature} We now introduce
a temperature parameter $T > 0$ to problem \eqref{eq:potts_upper_bound} which
divides $E({\bf x})$, or equivalently divides $\bf s$ belonging to $EP(F)$. Also, since $T > 0$, we can multiply the objective by $T$ leaving the problem unchanged. Without changing the solution, we can transform problem \eqref{eq:potts_upper_bound} as follows
\begin{equation}
    \min_{{\bf s} \in EP(F)} \quad g_T ({\bf s}) = \sum_{a = 1}^{N} T \cdot \log \sum_{i = 1}^L \exp(-\frac{s_{ai}}{T}).
\label{eq:potts_temp}
\end{equation}
\myparagraph{Worst-case Optimal Submodular Extension} 
We now connect our marginal estimation problem (\ref{eq:min_upper_bound}) with
LP relaxations using the following proposition.
{\proposition Using the $1$-of-$L$ encoding scheme, in the limit $T \to 0$,
  problem (\ref{eq:potts_temp}) for Potts model becomes:
\begin{align}
    - \min_{{\bf y} \in \Delta} f({\bf y}) 
\end{align}
where $f(.)$ is the Lovasz extension of $F(.)$.
\label{proposition:potts_equiv}}

@@

\begin{figure}
\centering
\includegraphics[scale = 0.30]{./figures/rhst_notation.png}
\mycaption{\footnotesize \em A hierarchical Potts model instance illustrating notations with 2 meta-labels (blue) and 4 labels (yellow). All labels are at the same level. $r = 2$, that is, edge-length decreases by 2 at each level. Also, distance between labels 1 and 3 is $d(1, 3) = 0.5 + 1 + 1 + 0.5 = 3$.} 
\label{fig:rhst}
\end{figure}
Potts model imposes the same penalty for unequal assignment of labels to neighbouring variables, regardless of the label dissimilarity. A more natural approach is to vary the penalty based on how different the labels are. A hierarchical Potts model permits this by specifying the distance between labels using a tree with the following properties:
\vspace{2mm}
\begin{enumerate}
  \itemsep+1em 
\item The vertices are of two types: (i) the leaf nodes representing labels, and (ii) the non-leaf nodes, except the root, representing meta-labels.
\item The lengths of all the edges from a parent to its children are the same.
\item The lengths of the edges along any path from the root to a leaf decreases by a factor of at least $r \geq 2$ at each step.
\item The metric distance between nodes of the tree is the sum of the edge lengths on the unique path between them. 
\end{enumerate}
\vspace{2mm}
%
A subtree $T$ of an hierarchical Potts model is a tree comprising all the descendants of some node $v$ (not root). Given a subtree $T$, $l_T$ denotes the length of the tree-edge leading upward from the root of $T$ and $L(T)$ denotes the set of leaves of $T$. We call the leaves of the tree as labels and all other nodes of the tree expect the root as \emph{meta-labels}. Figure \ref{fig:rhst} illustrates the notations in the context of a hierarchical Potts model.
%
\myparagraph{Tightest LP Relaxation} We use the same indicator variables $y_{ai}$ that were employed in the LP relaxation of Potts model. Let $y_a(T) = \sum_{i \in L(T)} y_{ai}$. The following LP relaxation is the tightest known for hierarchical Potts model in the worst-case, assuming the Unique Games Conjecture to be true \citep{manokaran2008sdp}
\begin{align}
\text{(T-LP)} \quad \min_{\bf y} \enskip & \widetilde{E}({\bf y}) =  \sum_{a} \sum_{i} \phi_a(i)y_{ai} + \nonumber\\
                                         &\sum_{(a, b) \in {\mathcal N}} w_{ab} \sum_T l_T \cdot |y_{a}(T) - y_{b}(T)| \nonumber\\
    \text{such that} \quad &{\bf y} \in \Delta.
\label{eq:t-lp}
\end{align}
The set $\Delta$ is the same domain as defined in equation (\ref{eq:delta}).

@@

Since any finite metric space can be probabilistically approximated by mixture
of tree metric \citep{bartal1996probabilistic}, the worst-case optimal
submodular extension for metric energies can be obtained using $F_{hier}$. Note
that $F_{hier}$ reduces to $F_{Potts}$ for Potts model. One can see this by
considering the Potts model as a star-shaped tree with edge weights as 0.5.
\begin{figure}
\centering
\begin{tabular}{cc}
\includegraphics[scale = 0.16]{./figures/synthetic_tree.png} &
\includegraphics[scale = 0.16]{./figures/synthetic_tree_2_new.png} \\
  \scriptsize(a) Tree A & \scriptsize(b) Tree B \\
\end{tabular}
\mycaption{\footnotesize \em The hierarchical Potts models defining pairwise
distance among 20 labels used for upper-bound comparison with TRW. Blue nodes
are the meta-labels and yellow nodes are labels. All the edges at a particular
level have the same edge weights. The sequence of weights from root level to
leaf level is 1, 0.5 for tree A and 1, 1, 0.5 for tree B. The yellow node is
shown to clump together 4 and 5 leaf nodes for tree A and B respectively.} 
\label{fig:syn_rhst}
\end{figure}

@@

\begin{figure}
\centering
\resizebox{150pt}{120pt}{
\begin{tikzpicture}[-latex ,auto ,node distance =2 cm and 2cm ,on grid
  , semithick , state/.style ={ circle , color = black , draw,black , text=blue , minimum width =1 cm}, cross/.style={color=red, very thick, dashed}, unary/.style={color=blue, very thick}]

@@

%\begin{figure}
%       \Tree [.root [.{m0} 0-3 ] [.{m1} 4-7 ] [.{m2} 8-11 ] [.{m3} 12-15 ] [.{m4} 16-19 ]]
%   %    \Tree [.root [.{m0} 0 1 2 3 ] [.{m1} 4 5 6 7 ] [.{m2} 8 9 10 11 ] [.{m3} 12 13 14 15 ] [.{m4} 16 17 18 19 ]]
%%    \Tree[. [. [.1 .2 .3]]]
%\mycaption{\footnotesize \em An $r$-HST defining pairwise distance among 20 labels used for upper-bound comparison with TRW. $m0$ stands for meta-label 0, and so on.}
%\label{fig:syn_rhst}
%\end{figure}
\begin{figure}
\centering
\includegraphics[scale = 0.50]{./figures/synthetic_upper_bound_comparison.pdf}
\mycaption{\footnotesize \em Upper-bound comparison using synthetic data. The
plot shows the ratio (Submod bound - TRW bound)/|TRW bound| averaged over 100
unary instances as a function of pairwise weights using the worst-case optimal and
alternate extension for Potts and hierarchical Potts models. We observe that
the worst-case optimal extension
(solid) results in tighter bounds as compared to the respective alternate
extensions (dotted). Also, the worst-case optimal extension bounds are in
similar range as the TRW bounds.}
\label{fig:syn_plot}
\end{figure}

@@

\myparagraph{Results} Figure \ref{fig:stereo} shows some example solutions obtained by picking the
label with maximum marginal probability for each variable for mean-field and
for our algorithm. We also report the time and energy values of the solution
for both methods. Though we are not performing MAP estimation, energy values
give us a quantitative indication of the quality of solutions. For the full set of
21 image pairs (2006 dataset), the average ratio of the energies of the solutions from our method 
compared to mean-field is 0.943. The avearge time ratio is 10.66. We observe that our algorithm results in more natural looking stereo matching results with lower energy values for all images. However, mean-field runs faster than our method for each instance.

\begin{figure*}
    \centering
\begin{tabular}{cccccc}
        \includegraphics[scale = 0.22]{\imagePath/stereo/higher_potts/tsukuba_GT} &
        \includegraphics[scale = 0.22]{\imagePath/stereo/higher_potts/tsukuba_hop} &
        \includegraphics[scale = 0.34]{\imagePath/stereo/higher_potts/baby1_GT} &
        \includegraphics[scale = 0.16]{\imagePath/stereo/higher_potts/baby1_hop} &
        \includegraphics[scale = 0.34]{\imagePath/stereo/higher_potts/flowerpots_GT} &
        \includegraphics[scale = 0.16]{\imagePath/stereo/higher_potts/flowerpots_hop} \\
        \scriptsize(a) Tsukuba GT & \scriptsize(b) Submod solution
        & \scriptsize(a) Baby1 GT & \scriptsize(b) Submod solution
        & \scriptsize(a) Flowerpots GT & \scriptsize(b) Submod solution\\
\end{tabular}
%\vspace{2mm}
\mycaption{\footnotesize \em Stereo matching using dense CRFs with higher-order
  Potts term in addition to Potts compatibility and Gaussian pairwise potentials.}
\label{fig:stereo_hop}
\end{figure*}

@@

\myparagraph{Method} We again use the modified Gaussian filtering implementation for dense CRFs by
\citep{ajanthan2017efficient} to compute the conditional gradient at each step.
To compute the contribution of the higher-order Potts, we make use of an
efficient strategy to reuse computation. Recall that computing the conditional
gradient coordinates $s^*_{\sigma(i)}$ requires us to obtain differences of the
nested sets $F(S_i) - F(S_{i - 1})$. We store the clique state at each $i$, and
this enables us to compute the difference for each coordinate in a constant
amount of time. In this case, computation of conditional gradient takes
$\mathcal{O}(cNL)$ where $c$ is the number of hihger-order cliques.

\myparagraph{Results} Figure \ref{fig:stereo_hop} shows some example solutions obtained by picking the
label with maximum marginal probability for each variable. We observe that our method gives results that are reasonably close to the ground-truth.

>>>>

In this work, we establish a hitherto unknown connection between the submodular
extension of the Potts model proposed by Zhang et al.\citep{zhang2015higher}, and the
objective function of an accurate linear programming (LP) relaxation of the
corresponding MAP estimation problem~\citep{kleinberg2002approximation}. This
connection has three important practical consequences. First, it establishes
the accuracy of the submodular extension of the Potts model, via the
UGC-hardness worst-case optimality of the LP relaxation. Second, it provides an
accurate submodular extension of the hierarchical Potts model, via the LP
relaxation of the corresponding MAP estimation problem proposed
by Kleinberg and Tardos \citep{kleinberg2002approximation}. Since any metric can be accurately
approximated as a mixture of hierarchical Potts
models~\citep{bartal1996probabilistic, bartal1998approximating}, this result
also provides a computationally feasible algorithm for estimating the marginals
for metric labeling. Third, it establishes the equivalence between the
subgradient of the LP relaxation and the conditional gradient of the problem of
minimising the upper bound of the log-partition. This allows us to employ the
widely used dense CRF, since the subgradient of its LP relaxation can be
efficiently computed using a recently proposed modified Gaussian filtering
algorithm~\citep{ajanthan2017efficient}. As a consequence, we provide the first
efficient algorithm to compute an upper bound of the log-partition function of
dense CRFs. This provides complementary information to the popular mean-field
inference algorithm for dense CRFs, which computes a lower bound on the
log-partition ~\citep{koltun2011efficient}. Finally, we also obtain the
submodular extension based on the LP relaxation for a higher-order version of
the Potts model that captures useful image statistics.  We show that the quality of our
solution is comparable to tree reweighted message passing (TRW)
~\citep{wainwright2005new} for the case of sparse CRFs. Unlike our approach,
TRW is computationally infeasible for dense CRFs, thereby limiting its use in
practice. Using dense CRF models, we perform stereo matching on standard
data sets and obtain better results than \citep{koltun2011efficient}. The complete code is available at \url{https://github.com/pankajpansari/denseCRF}.

@@

\myparagraph{Set Encoding} We choose to use the $1$-of-$L$ encoding for Potts model as described in section \ref{sec:review}. With the encoding scheme for Potts model above, $g({\bf s})$ can be factorised and problem (\ref{eq:min_upper_bound}) can be rewritten as:
%
\begin{equation}
\min_{{\bf s} \in EP(F)} \quad \sum_{a = 1}^{N} \log \sum_{i = 1}^L \exp(-s_{ai}).
\label{eq:potts_upper_bound}
\end{equation}
(See Remark 1 in appendix)
\myparagraph{Marginal Estimation with Temperature} We now introduce
a temperature parameter $T > 0$ to problem \eqref{eq:potts_upper_bound} which
divides $E({\bf x})$, or equivalently divides $\bf s$ belonging to $EP(F)$. Also, since $T > 0$, we can multiply the objective by $T$ leaving the problem unchanged. Without changing the solution, we can transform problem \eqref{eq:potts_upper_bound} as follows
\begin{equation}
    \min_{{\bf s} \in EP(F)} \quad g_T ({\bf s}) = \sum_{a = 1}^{N} T \cdot \log \sum_{i = 1}^L \exp(-\frac{s_{ai}}{T}).
\label{eq:potts_temp}
\end{equation}

\begin{figure}
\centering
\includegraphics[scale = 0.30]{./figures/potts_chain_extension.png}
\mycaption{\footnotesize \em An illustration of the worst-case optimal
submodular extension for Potts model for a chain graph of 4 variables, each of
which can take 3 labels. The figure shows the way to compute the extension
values of the set $A = \{v_{1, 1}, v_{4, 1}, v_{3, 2}$\}.}
\label{fig:alternate}
\end{figure}

\begin{figure}
\centering
\resizebox{180pt}{150pt}{
\begin{tikzpicture}[-latex ,auto, node distance =1.5 cm and 1.5cm ,on grid
  , semithick , state/.style ={ circle , color = black , draw,black , text=blue , minimum width =1 cm}, cross/.style={color=red, very thick, dashed}, unary/.style={color=blue, very thick}]

@@

\myparagraph{Worst-case Optimal Submodular Extension} 
We now connect our marginal estimation problem (\ref{eq:min_upper_bound}) with
LP relaxations using the following proposition.
{\proposition Using the $1$-of-$L$ encoding scheme, in the limit $T \to 0$,
  problem (\ref{eq:potts_temp}) for Potts model becomes:
\begin{align}
    - \min_{{\bf y} \in \Delta} f({\bf y}) 
\end{align}
where $f(.)$ is the Lovasz extension of $F(.)$.
\label{proposition:potts_equiv}}

@@

Potts model imposes the same penalty for unequal assignment of labels to neighbouring variables, regardless of the label dissimilarity. A more natural approach is to vary the penalty based on how different the labels are. A hierarchical Potts model permits this by specifying the distance between labels using a tree with the following properties:
\vspace{2mm}
\begin{enumerate}
  \itemsep+1em 
\item The vertices are of two types: (i) the leaf nodes representing labels, and (ii) the non-leaf nodes, except the root, representing meta-labels.
\item The lengths of all the edges from a parent to its children are the same.
\item The lengths of the edges along any path from the root to a leaf decreases by a factor of at least $r \geq 2$ at each step.
\item The metric distance between nodes of the tree is the sum of the edge lengths on the unique path between them. 
\end{enumerate}
\vspace{2mm}
%
\begin{figure}
\centering
\includegraphics[scale = 0.30]{./figures/rhst_notation.png}
\mycaption{\footnotesize \em A hierarchical Potts model instance illustrating notations with 2 meta-labels (blue) and 4 labels (yellow). All labels are at the same level. $r = 2$, that is, edge-length decreases by 2 at each level. Also, distance between labels 1 and 3 is $d(1, 3) = 0.5 + 1 + 1 + 0.5 = 3$.} 
\label{fig:rhst}
\end{figure}

A subtree $T$ of an hierarchical Potts model is a tree comprising all the descendants of some node $v$ (not root). Given a subtree $T$, $l_T$ denotes the length of the tree-edge leading upward from the root of $T$ and $L(T)$ denotes the set of leaves of $T$. We call the leaves of the tree as labels and all other nodes of the tree expect the root as \emph{meta-labels}. Figure \ref{fig:rhst} illustrates the notations in the context of a hierarchical Potts model.
%
\myparagraph{Tightest LP Relaxation} We use the same indicator variables $y_{ai}$ that were employed in the LP relaxation of Potts model. Let $y_a(T) = \sum_{i \in L(T)} y_{ai}$. The following LP relaxation is the tightest known for hierarchical Potts model in the worst-case, assuming the Unique Games Conjecture to be true \citep{manokaran2008sdp}
\begin{align}
\text{(T-LP)} \quad \min_{\bf y} \enskip & \widetilde{E}({\bf y}) =  \sum_{a} \sum_{i} \phi_a(i)y_{ai} + \nonumber\\
                                         &\sum_{(a, b) \in {\mathcal N}} w_{ab} \sum_T l_T \cdot |y_{a}(T) - y_{b}(T)| \nonumber\\
    \text{such that} \quad &{\bf y} \in \Delta.
\label{eq:t-lp}
\end{align}
The set $\Delta$ is the same domain as defined in equation (\ref{eq:delta}).

@@

Since any finite metric space can be probabilistically approximated by mixture
of tree metric \citep{bartal1996probabilistic}, the worst-case optimal
submodular extension for metric energies can be obtained using $F_{hier}$. Note
that $F_{hier}$ reduces to $F_{Potts}$ for Potts model. One can see this by
considering the Potts model as a star-shaped tree with edge weights as 0.5.

@@

%\begin{figure}
%       \Tree [.root [.{m0} 0-3 ] [.{m1} 4-7 ] [.{m2} 8-11 ] [.{m3} 12-15 ] [.{m4} 16-19 ]]
%   %    \Tree [.root [.{m0} 0 1 2 3 ] [.{m1} 4 5 6 7 ] [.{m2} 8 9 10 11 ] [.{m3} 12 13 14 15 ] [.{m4} 16 17 18 19 ]]
%%    \Tree[. [. [.1 .2 .3]]]
%\mycaption{\footnotesize \em An $r$-HST defining pairwise distance among 20 labels used for upper-bound comparison with TRW. $m0$ stands for meta-label 0, and so on.}
%\label{fig:syn_rhst}
%\end{figure}
\begin{figure}
\centering
\begin{tabular}{cc}
\includegraphics[scale = 0.25]{./figures/synthetic_tree.png} &
\includegraphics[scale = 0.25]{./figures/synthetic_tree_2_new.png} \\
  \scriptsize(a) Tree A & \scriptsize(b) Tree B \\
\end{tabular}
\mycaption{\footnotesize \em The hierarchical Potts models defining pairwise
distance among 20 labels used for upper-bound comparison with TRW. Blue nodes
are the meta-labels and yellow nodes are labels. All the edges at a particular
level have the same edge weights. The sequence of weights from root level to
leaf level is 1, 0.5 for tree A and 1, 1, 0.5 for tree B. The yellow node is
shown to clump together 4 and 5 leaf nodes for tree A and B respectively.} 
\label{fig:syn_rhst}
\end{figure}

\begin{figure}
\centering
\resizebox{180pt}{150pt}{
\begin{tikzpicture}[-latex ,auto ,node distance =2 cm and 2cm ,on grid
  , semithick , state/.style ={ circle , color = black , draw,black , text=blue , minimum width =1 cm}, cross/.style={color=red, very thick, dashed}, unary/.style={color=blue, very thick}]

@@

\begin{figure}
\centering
\includegraphics[scale = 0.50]{./figures/synthetic_upper_bound_comparison.pdf}
\mycaption{\footnotesize \em Upper-bound comparison using synthetic data. The
plot shows the ratio (Submod bound - TRW bound)/|TRW bound| averaged over 100
unary instances as a function of pairwise weights using the worst-case optimal and
alternate extension for Potts and hierarchical Potts models. We observe that
the worst-case optimal extension
(solid) results in tighter bounds as compared to the respective alternate
extensions (dotted). Also, the worst-case optimal extension bounds are in
similar range as the TRW bounds.}
\label{fig:syn_plot}
\end{figure}

@@

\myparagraph{Results} Figure \ref{fig:stereo} shows some example solutions obtained by picking the
label with maximum marginal probability for each variable for mean-field and
for our algorithm. We also report the time and energy values of the solution
for both methods. Though we are not performing MAP estimation, energy values
give us a quantitative indication of the quality of solutions. For the full set of
21 image pairs (2006 dataset), the average ratio of the energies of the solutions from our method 
compared to mean-field is 0.943. The avearge time ratio is 10.66. We observe that our algorithm results in more natural looking stereo matching results with lower energy values for all images. However, mean-field runs faster than our method for each instance.The set of hyperparameters that we used can be found in the
appendix.

\begin{figure*}
    \centering
\begin{tabular}{cccccc}
        \includegraphics[scale = 0.22]{\imagePath/stereo/higher_potts/tsukuba_GT} &
        \includegraphics[scale = 0.22]{\imagePath/stereo/higher_potts/tsukuba_hop} &
        \includegraphics[scale = 0.34]{\imagePath/stereo/higher_potts/baby1_GT} &
        \includegraphics[scale = 0.16]{\imagePath/stereo/higher_potts/baby1_hop} &
        \includegraphics[scale = 0.34]{\imagePath/stereo/higher_potts/flowerpots_GT} &
        \includegraphics[scale = 0.16]{\imagePath/stereo/higher_potts/flowerpots_hop} \\
        \scriptsize(a) Tsukuba GT & \scriptsize(b) Submod solution
        & \scriptsize(a) Baby1 GT & \scriptsize(b) Submod solution
        & \scriptsize(a) Flowerpots GT & \scriptsize(b) Submod solution\\
        {} & {} 
        & {} & \scriptsize 2476.82s
        & {} & \scriptsize 2471.58s\\

\end{tabular}
%\vspace{2mm}
\mycaption{\footnotesize \em Stereo matching using dense CRFs with higher-order
  Potts term in addition to Potts compatibility and Gaussian pairwise potentials.}
\label{fig:stereo_hop}
\end{figure*}

@@

\myparagraph{Method} We again use the modified Gaussian filtering implementation for dense CRFs by
\citep{ajanthan2017efficient} to compute the conditional gradient at each step.
To compute the contribution of the higher-order Potts, we make use of an
efficient strategy to reuse computation. Recall that computing the conditional
gradient coordinates $s^*_{\sigma(i)}$ requires us to obtain differences of the
nested sets $F(S_i) - F(S_{i - 1})$. We store the clique state at each $i$, and
this enables us to compute the difference for each coordinate in a constant
amount of time. In this case, computation of conditional gradient takes
$\mathcal{O}(cNL)$ where $c$ is the number of higher-order cliques. We ran our
algorithm for 200 iterations.

\myparagraph{Results} Figure \ref{fig:stereo_hop} shows some example solutions
obtained by picking the label with maximum marginal probability for each
variable. We observe that our method gives results that are reasonably close to
the ground-truth. The set of hyperparameters that we used can be found in the
appendix.
